% !TeX program = xelatex
\documentclass{custhesis}

\custserial{}
\custdoctype{本科生毕业设计}
\custheadertitle{长春理工大学本科生毕业设计}
\custtitle{改进粒子群优化算法研究}
\custenglishtitle{Research on an Improved Particle Swarm Optimization Algorithm}
\custstudent{}
\custmajor{}
\custstudentid{}
\custsupervisor{}
\custschool{}
\custdate{二〇二六年六月}

\begin{document}

\makecustcover
\makecustdeclaration

\custfrontmatter

\begin{custcnabstract}
本文以智能优化算法研究为示例背景，围绕问题建模、基准算法分析、改进策略设计、实验方案和结果评价等环节，给出一套适用于计算机类算法研究方向本科毕业设计写作的示例性论文结构。示例内容以粒子群优化算法为基础，说明动态参数调整、搜索策略改进和实验对比分析的常见写法，并通过图表、公式和三线表展示常用论文元素的排版方式。

本文内容仅作为模板示例，重点展示长春理工大学计算机科学技术学院本科毕业设计中常见的版式、章节层级、图表编号、公式编号、参考文献和附录组织方式。实际使用时，应根据具体算法、数据集、实验结果和分析结论替换相应内容。
\custkeywords{粒子群优化\quad 启发式算法\quad 参数寻优\quad 收敛分析\quad 实验对比}
\end{custcnabstract}

\begin{custenabstract}
This template demonstrates a common thesis structure for undergraduate algorithm research in computer science. The sample topic is based on particle swarm optimization and covers problem modeling, baseline analysis, improvement strategy design, experimental setup, and result evaluation. It also provides examples of figures, tables, equations, references, appendices, and acknowledgements.

The sample text is intended only for formatting and structural reference. Users should replace the abstract, algorithm description, experimental results, and references with materials from their own projects before submission.
\custkeywordsen{particle swarm optimization; heuristic algorithm; parameter tuning; convergence analysis; experimental comparison}
\end{custenabstract}

\custtableofcontents

\custmainmatter

\input{chapters/chapter1}
\input{chapters/chapter2}
\input{chapters/conclusion}

\begin{custbibliography}
  \item 作者. 智能优化算法原理与应用[M]. 出版地: 出版社, 出版年: 起止页码.
  \item 作者. 改进粒子群优化算法研究[J]. 期刊名, 出版年份, 卷号(期号): 起止页码.
  \item Author A, Author B, Author C, et al. An improved heuristic optimization algorithm[J]. Journal Name, Year, Volume(Issue): pages.
  \item GB/T 7714-2015, 信息与文献 参考文献著录规则[S]. 北京: 中国标准出版社, 2015.
\end{custbibliography}

\custappendixstart
\input{appendices/appendix-a}

\begin{custacknowledgements}
这里填写致谢内容。致谢应简洁、真实，可对指导教师以及在毕业设计过程中给予帮助的组织和个人表示感谢。正式提交前请删除本段说明文字。
\end{custacknowledgements}

\end{document}
